Manuscript

### 2018-12-07 manuscript.Rmd
remade all lineage plotlys/pngs, updated signif Rds files

```{r}
library(bsselectR)
library(cowplot)
theme_set(theme_light())
library(data.table)
library(ggpubr)
library(ggrepel)
library(gridExtra)
library(ggsignif)
library(htmlwidgets)
library(kableExtra)
library(plotly)
library(reshape2)
library(scales)
library(tidyverse)
```

@@

## Make G2P lineage Pearson plotlys
```{r}
PearsonPlotlyByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(signif_all_lin, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

@@

knitr::kable(ccle_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

knitr::kable(ctrp_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

knitr::kable(gdsc_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)

@@

crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
  facet_grid(~ Metric) +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  coord_cartesian(ylim = c(0, 50)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

@@

#### Summary: Test plots

```{r fig.height=4, fig.width=12}
ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
ccle_res_mut$corr <- 0
ccle_res_mut$Metric <- "Mutation Status"
ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
ccle_res_mut$Dataset <- "CCLE"
ccle_pearson_res_GE <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_GE$Metric <- "Gene Expression"
subset(ccle_pearson_res_GE, p < 0.05)
ccle_pearson_res_CN <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_CN$Metric <- "Copy Number"
subset(ccle_pearson_res_CN, p < 0.05)
ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)

@@

```{r fig.height=6, fig.width=12}
ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
ctrp_res_mut$corr <- 0
ctrp_res_mut$Metric <- "Mutation Status"
ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
ctrp_res_mut$Dataset <- "CTRP"
ctrp_pearson_res_GE <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_GE$Metric <- "Gene Expression"
subset(ctrp_pearson_res_GE, p < 0.05)
ctrp_pearson_res_CN <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_CN$Metric <- "Copy Number"
subset(ctrp_pearson_res_CN, p < 0.05)
ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)

ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene_Ordered, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

@@

```{r}
ccle_druggenelin_summ <- ccle_signif_g2p_lineage
ccle_druggenelin_summ$Drug_Gene <- paste0(ccle_druggenelin_summ$Drug, "_", ccle_druggenelin_summ$Hugo_Symbol)
ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
ccle_druggenelin_summ$Dataset <- "CCLE"

ctrp_druggenelin_summ <- ctrp_signif_g2p_lineage
ctrp_druggenelin_summ$Drug_Gene <- paste0(ctrp_druggenelin_summ$Drug, "_", ctrp_druggenelin_summ$Hugo_Symbol)
ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
ctrp_druggenelin_summ$InG2P <- ifelse(ctrp_druggenelin_summ$n != 0, "Yes", "No")
ctrp_druggenelin_summ$Dataset <- "CTRP"

gdsc_druggenelin_summ <- gdsc_signif_g2p_lineage
gdsc_druggenelin_summ$Drug_Gene <- paste0(gdsc_druggenelin_summ$Drug, "_", gdsc_druggenelin_summ$Hugo_Symbol)
gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
gdsc_druggenelin_summ$InG2P <- ifelse(gdsc_druggenelin_summ$n != 0, "Yes", "No")
gdsc_druggenelin_summ$Dataset <- "GDSC"
g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P, levels = c("Yes", "No"))
# test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
# test <- test[-39,]
```

@@

```{r, eval=FALSE}
ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
ccle_signif_ge_all_lin$Dataset <- "CCLE"
ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
ccle_signif_cn_all_lin$Dataset <- "CCLE"
ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

>>>>

```{r}
library(bsselectR)
library(cowplot)
theme_set(theme_light())
library(data.table)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(gplots)
library(gridExtra)
library(htmlwidgets)
library(kableExtra)
library(plotly)
library(reshape2)
library(scales)
library(tidyverse)
library(VennDiagram)
```

@@

## Make G2P lineage Pearson plotlys
```{r}
PearsonPlotlyByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(signif_lin_g2p_grid, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

@@

knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

@@

```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
subset(crispr_res_mut, p < 0.05)

@@

crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
  facet_grid(~ Metric) +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  coord_cartesian(ylim = c(0, 50)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

@@

#### Summary: Drug screen test plots

```{r fig.height=4, fig.width=12}
ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
ccle_res_mut$corr <- 0
ccle_res_mut$Metric <- "Mutation Status"
ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
ccle_res_mut$Dataset <- "CCLE"
ccle_pearson_res_GE <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_GE$Metric <- "Gene Expression"
subset(ccle_pearson_res_GE, p < 0.05)
ccle_pearson_res_CN <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_CN$Metric <- "Copy Number"
subset(ccle_pearson_res_CN, p < 0.05)
ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)

@@

```{r fig.height=6, fig.width=12}
ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
ctrp_res_mut$corr <- 0
ctrp_res_mut$Metric <- "Mutation Status"
ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
ctrp_res_mut$Dataset <- "CTRP"
ctrp_pearson_res_GE <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_GE$Metric <- "Gene Expression"
subset(ctrp_pearson_res_GE, p < 0.05)
ctrp_pearson_res_CN <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_CN$Metric <- "Copy Number"
subset(ctrp_pearson_res_CN, p < 0.05)
ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)

ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

@@

```{r}
ccle_druggenelin_summ <- ccle_signif_grid_lineage
ccle_druggenelin_summ$Drug_Gene <- paste0(ccle_druggenelin_summ$Drug, "_", ccle_druggenelin_summ$Hugo_Symbol)
ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
ccle_druggenelin_summ$Dataset <- "CCLE"

ctrp_druggenelin_summ <- ctrp_signif_grid_lineage
ctrp_druggenelin_summ$Drug_Gene <- paste0(ctrp_druggenelin_summ$Drug, "_", ctrp_druggenelin_summ$Hugo_Symbol)
ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
ctrp_druggenelin_summ$InG2P <- ifelse(ctrp_druggenelin_summ$n != 0, "Yes", "No")
ctrp_druggenelin_summ$Dataset <- "CTRP"

gdsc_druggenelin_summ <- gdsc_signif_grid_lineage
gdsc_druggenelin_summ$Drug_Gene <- paste0(gdsc_druggenelin_summ$Drug, "_", gdsc_druggenelin_summ$Hugo_Symbol)
gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
gdsc_druggenelin_summ$InG2P <- ifelse(gdsc_druggenelin_summ$n != 0, "Yes", "No")
gdsc_druggenelin_summ$Dataset <- "GDSC"
g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P, levels = c("Yes", "No"))
# test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
# test <- test[-39,]
```

@@

DGL overlap:
```{r}
dgl_overlap_test_list <- list(CCLE = unique(ccle_data_g2p_dgl$Drug_Gene_Lin),
                              CTRP = unique(ctrp_data_g2p_dgl$Drug_Gene_Lin),
                              GDSC = unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))

ItemsList <- venn(dgl_overlap_test_list, show.plot=TRUE)
```

Test the 102 level-A G2P drug-gene-lineage combinations:
```{r, eval=FALSE}
ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name)))]
ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_dgl)
ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
ccle_signif_ge_all_lin$Dataset <- "CCLE"
ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_dgl)
ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
ccle_signif_cn_all_lin$Dataset <- "CCLE"
ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name)))]
ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_dgl)
ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
ctrp_signif_ge_all_lin$Dataset <- "CTRP"
ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_dgl)
ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
ctrp_signif_cn_all_lin$Dataset <- "CTRP"
ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name)))]
gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_dgl)
gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
gdsc_signif_ge_all_lin$Dataset <- "GDSC"
gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_dgl)
gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
gdsc_signif_cn_all_lin$Dataset <- "GDSC"
gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
saveRDS(signif_all_lin, "./data_munging/rds/signif_lin_g2p_dgl.rds")
```

```{r}
signif_lin_g2p_dgl <- readRDS("./data_munging/rds/signif_lin_g2p_dgl.rds")

# CCLE mut, n = 7
ccle_mut <- filter(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
ccle_mut_n <- nrow(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p))
# CCLE GE/CN, n = 9
ccle_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
ccle_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
ccle_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CCLE"))
ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           CCLE_p = p,
                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
                                           CCLE_r_GE = Pearson_Corr_GE,
                                           CCLE_p_GE = Pearson_Pval_GE,
                                           CCLE_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ccle_Pear_n, "Sig", NA),
                                           CCLE_r_CN = Pearson_Corr_CN,
                                           CCLE_p_CN = Pearson_Pval_CN,
                                           CCLE_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ccle_Pear_n, "Sig", NA)))

# CTRP mut, n = 48
ctrp_mut <- filter(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
ctrp_mut_n <- nrow(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p))
# CTRP GE/CN, n = 61
ctrp_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
ctrp_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
ctrp_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CTRP"))
ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           CTRP_p = p,
                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
                                           CTRP_r_GE = Pearson_Corr_GE,
                                           CTRP_p_GE = Pearson_Pval_GE,
                                           CTRP_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ctrp_Pear_n, "Sig", NA),
                                           CTRP_r_CN = Pearson_Corr_CN,
                                           CTRP_p_CN = Pearson_Pval_CN,
                                           CTRP_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ctrp_Pear_n, "Sig", NA)))

# GDSC mut, n = 39
gdsc_mut <- filter(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
gdsc_mut_n <- nrow(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p))
# GDSC GE/CN, n = 53
gdsc_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
gdsc_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
gdsc_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "GDSC"))
gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           GDSC_p = p,
                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
                                           GDSC_r_GE = Pearson_Corr_GE,
                                           GDSC_p_GE = Pearson_Pval_GE,
                                           GDSC_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / gdsc_Pear_n, "Sig", NA),
                                           GDSC_r_CN = Pearson_Corr_CN,
                                           GDSC_p_CN = Pearson_Pval_CN,
                                           GDSC_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / gdsc_Pear_n, "Sig", NA)))

dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
```

Test all combinations of G2P drugs and genes in all lineages. InG2P indicates G2P drug-gene associations test across all lineages.
```{r, eval=FALSE}
ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
ccle_signif_ge_all_lin$Dataset <- "CCLE"
ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
ccle_signif_cn_all_lin$Dataset <- "CCLE"
ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
